\huge A Usability Evaluation of Tor Launcher

### 2017-03-03 pets2017-paper/pets2017-paper.tex
Added a better description of conditions

\subsection{Observations}
We noticed that the interface leaves a lot of freedom for error but does not give good instructions on when there is an error and how to fix it: \\

\begin{itemize}
\item {\bfseries Difficult tasks:} The interface uses technical and Tor-specific terms that are likely to be unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports. 
\item {\bfseries Too many choices:}  Users who do not need a bridge or proxy are able to configure them. There are nine choices for bridges by transport and more options to input a custom bridge. Almost any HTTP or SOCKS proxy can be used as the proxy. Custom bridge lines require the bridge information with specific syntax, but this syntax is not specified in the interface. Proxy fields also do not provide syntactic guidelines. See the whole list of possible errors in Appendix~\ref{states}. 
\item {\bfseries Poor feedback:} Even if there was a syntactic error in the bridge or proxy fields, the user is not notified until after a connection is attempted and fails. If a censored bridge was chosen, the connection timeout takes several minutes. Error messages were often technical and did not give suggestions.
\end{itemize}

@@

\subsection{Recruitment}
We recruited people from Craigslist using an ad (Appendix~\ref{qualitative-recruitment}) and prescreening survey (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} so that we could have a diversity of gender, age, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). Our age calculations omit one participant who declined to report it. All of our users had at least some college education. Twelve were new users and 4 had previously used Tor Browser in some capacity.

>>>>

\subsection{Observations}
We noticed that the interface leaves a lot of freedom for error while not giving good instructions on how to recover from errors: \\

\begin{itemize}
\item {\bfseries Technical terms:} The interface uses technical and Tor-specific terms that are likely unfamiliar to an average user (e.g., ``Tor network,'' ``local proxy,'' ``bridges,'' and ``transports''). 
\item {\bfseries Too many choices:}  Users who do not need a bridge or proxy are able to configure them. There are nine choices for bridges by transport and more options to input a custom bridge. Almost any HTTP or SOCKS proxy can be used as the proxy. Custom bridge lines require the bridge information with specific syntax, but this syntax is not specified in the interface. Proxy fields also do not provide syntactic guidelines. See the whole list of possible errors in Appendix~\ref{states}. 
\item {\bfseries Poor feedback:} Even if there was a syntactic error in the bridge or proxy fields, the user is not notified until after a connection is attempted and fails. If a censored bridge was chosen, the connection timeout takes several minutes. Error messages were often technical and did not give suggestions.
\end{itemize}

@@

\subsection{Recruitment}
We recruited people from Craigslist using an ad (Appendix~\ref{qualitative-recruitment}) and prescreening survey (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} so that we could have a diversity of gender, age, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). Our age statistics omit one participant who declined to disclose. All of our participants had at least some college education. Twelve were new users and 4 had previously used Tor Browser in some capacity.
